FMA: A Dataset For Music Analysis

### 2017-02-15 paper_FMA_nov2016.tex
Acknowledgments
update web links

\documentclass[a4paper,12pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage[top=1in,bottom=2in,left=1in,right=1in]{geometry}
\usepackage{graphicx} \graphicspath{{figures/}}
\usepackage{subfigure}
\usepackage{color}
\usepackage[normalem]{ulem}

@@

@@

\noindent
{\bf Availability and reproducible research.} The 3 proposed FMA datasets are available at\\

 \url{https://lts2.epfl.ch/datasets/fma}\\

 \noindent
 We also provide IPython notebooks at this address\\

@@

 \noindent
 to load the datasets and to start using them for research purposes.\\

\noindent
{\bf Potential applications.} We foresee multiple applications of this new dataset. The most obvious one is for music analysis with deep learning techniques. As raw music tracks are available, deep learning techniques like convolutional neural networks \cite{pro:LeCunBottouBengioHaffner98MNIST} and recurrent neural networks \cite{art:HochreiterSchmidhuber97LSTM} can be directly applied. Besides, standard data analysis tasks such as classification, clustering, regression, text analysis, visualization can also be applied to this new music dataset.\\

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{fancyhdr}
\usepackage[colorlinks=true,allcolors=blue]{hyperref}
\usepackage[top=1in,bottom=2in,left=1in,right=1in]{geometry}
\usepackage{graphicx} \graphicspath{{figures/}}
\usepackage{subfigure}
\usepackage{color}
\usepackage[normalem]{ulem}

@@

% TODO
% Problems
% Genre classif / mutli-genre classif
% Recommendation
% Play count prediction

@@

\paragraph{Availability and reproducible research.}

All the datasets as well as Jupyter notebooks used to produce them, the
analysis, and baselines as are available online at

@@

 Code to support the use of the data is provided as well.

\paragraph{Potential applications.} We foresee multiple applications of this new dataset. The most obvious one is for music analysis with deep learning techniques. As raw music tracks are available, deep learning techniques like convolutional neural networks \cite{pro:LeCunBottouBengioHaffner98MNIST} and recurrent neural networks \cite{art:HochreiterSchmidhuber97LSTM} can be directly applied. Besides, standard data analysis tasks such as classification, clustering, regression, text analysis, visualization can also be applied to this new music dataset.\\

\section*{Acknowledgments}

We are grateful to SWITCH and EPFL for hosting the dataset within the context
of the \href{https://projects.switch.ch/scale-up/}{SCALE-UP} project, funded in
part by the swissuniversities \href{http://www.swissuniversities.ch/isci}{SUC
P-2 program}.
